Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2014-09-11 paper.tex
use alternate plot of most intense cluster

%Max vorticity clustering.
One of the applications of thresholding in turbulence is to find the locations of maximum vorticity in a particular time-step or the dataset as a whole.
The locations of maximum vorticity are usually associated with the most intense vortices in the dataset and often have interesting and complex
reconnection events associated with them. 
Once obtained from the service, these locations can be clustered in both 3d and 4d. This allows scientists to examine their evolution with the flow
and make subsequent analysis queries as needed in order to study these events. The relationship between different worms that connect and reconnect
at those locations is of the most interest.

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.35in]{Figures/most_intense_cluster.png}
\caption{3D (fixed frame) cut through the 4D cluster containing the most intense event.
Lines parallel to the axes are given for reference: red, green and blue correspond to $x$, $y$ and $z$, respectively;
their lengths are the extents of the structure on each axis, which are approximately $0.55 \pi \times 0.40 \pi \times 0.17 \pi$.}
\label{fig:max_vort_cluster}
\end{figure}

>>>>

%Max vorticity clustering.
One of the applications of thresholding in turbulence is to find the locations of maximum vorticity in a particular time-step or the dataset as a whole.
The locations of maximum vorticity are usually associated with the most intense vortices in the dataset and often have interesting and complex
reconnection events associated with them. 
Once obtained from the service, these locations can be clustered in both 3d and 4d. This allows scientists to examine their evolution with the flow
and make subsequent analysis queries as needed in order to study these events. The relationship between different ``worms'' (see figure \ref{fig:max_vort_cluster}) that connect and reconnect
at those locations is of the most interest.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=7in]{Figures/most_intense_cluster_alt.pdf}
\caption{3D (fixed frame) cut through the 4D cluster containing the most intense event.}
\label{fig:max_vort_cluster}
\end{figure*}
